Learning \strips\ Action Models from State-Constraints

### 2017-12-04 doc/ijcai-18/constraints-learning.tex
updating the sketch for the ijcai18 paper

\title{Learning Strips Action Models from State-Constraints}

@@

\begin{abstract}
This paper presents a classical planning compilation for learning \strips\ action models from observations of plan executions. Interestingly the input to the compilation is a set of {\em state-constraints} that bounds the space of possible action models and that does not require the precise executed actions. The output is a possible action \strips\ action model, that satisfies the given state-constraints. Last but not least, the paper shows that our compilation is also extensible to include further information about the observed plan executions to increase the accuracy of the learned models.  
\end{abstract}

@@

Learning \strips\ action models from observations of plan executions is a well-studied problem with sophisticated algorithms, like {\sc ARMS}~\cite{yang2007learning}, {\sc SLAF}~\cite{amir:alearning:JAIR08} or {\sc LOCM}~\cite{cresswell2013acquiring}. Motivated by recent advances on the synthesis of different kinds of generative models with classical planning~\cite{bonet2009automatic,segovia2016hierarchical,segovia2017generating}, this paper introduces an innovative approach for learning \strips\ action models from observations of plan executions that:
\begin{enumerate}
\item Does not require information about the the precise applied actions.
\item Can be defined as a classical planning compilation which opens the door to the bootstrapping of planning action models.
\item Is extensible to include further information about the observed plan executions to increase the accuracy of the learned models.
\end{enumerate}

@@

\subsection{State-constraints}
A {\em state invariant} is a formula $\phi$ that holds in the initial state, formally $I\models \phi$, and at any state reachable from that state~\cite{rintanen:schematicInvariants:AAAI2017}, for all states $s$ reachable from $I$ $s\models \phi$.

A {\em mutex} is a particualr case of state invariant that take the form of a binary clause and that represents that a pair of different properties cannot be simultaneously true and are hence mutually exclusive. For instance, in a three-blocks blocksworld $on(block1,block2)$ and $on(block1,block3)$ are mutex.

A {\em domain invariant} is a particular state invariant that does not depend on a particular initial state, since they are instance-independent~\cite{kautz:mutex:IJCAI1999}. A {\em lifted invariant} is a state invariant defined usig a first order formula over the predicates of a given planning domain~\cite{rintanen:schematicInvariants:AAAI2017}. For instance in the blocksworld, $\forall x,y,z\ (on(x,y)\wedge on(x,z)) \implies y=z$, is a domain and lifted invariant because a block can only be on top of a single block no matter the initial state  and no matter the block.

Now we are ready to define a particular case of state-constraints called {\em lifted domain mutex} as a lifted domain invariant that takes the form of a binary clause. For instance, in the blocksworld $\forall x,y$ then $clear(x)$ and $on(x,y)$ is a {\em lifted domain mutex}.

{\em Linear Temporal Logic} (LTL) includes model operator that also allows to represent state constraints~\cite{haslum:LTL:ecai10}. For instance the {\em always} operator, denoted by $\square$, defines constraints that, like {\em lifted domain invariants}, must be true at any reachable state.

\section{Learning \strips\ action models}
Learning \strips\ action models from fully available input knowledge, i.e. from plans where the {\em pre-} and {\em post-states} of every action in a plan are available, is straightforward. When any intermediate state is available, \strips\ operator schemes are derived lifting the literals that change between the pre and post-state of the corresponding action executions. Preconditions are derived lifting the minimal set of literals that appears in all the pre-states of the corresponding actions.

This section formalizes more challenging learning tasks, where less input knowledge is available:

\subsubsection{Learning from state-constraints.} This learning task corresponds to observing an agent acting in the world but watching only the results of its plan executions. No information about the actions in the plans is given. This learning task is formalized as $\Lambda=\tup{\Psi,\Sigma,\Phi}$:
\begin{itemize}
\item $\Psi$ is the set of predicates that define the abstract state space of a given planning domain.
\item $\Sigma=\{\sigma_1,\ldots,\sigma_{\tau}\}$ is a set of state sequences $\sigma_t=(s_0^t,s_1^t,\ldots,s_{n}^t)$ such that,  {\small $1\leq i\leq n$} and {\tt\small $1\leq t\leq \tau$}, comprises the states resulting from executing an unknown plan $\pi_t$ starting from the {\em initial} state $s_0^t$.
\item $\Phi$ is a set of {\em lifted domain mutex}.
\end{itemize}

A solution to $\Lambda$ is a set of operator schema $\Xi$ that is compliant with the predicates in $\Psi$, the given set of states $\Sigma$ and the set of state constraints $\Phi$. In this learning scenario, a solution must not only determine a possible \strips\ action model but also the plans $\pi_t$, {\tt\small $1\leq t\leq \tau$} that explain the given set of states $\Sigma$ using the learned \strips\ model.

@@

\begin{subfigure}{.6\textwidth}
{\tt ;;; Label $\Phi$}
\begin{lstlisting}[mathescape]
(:derived (invariant-1-1)
  (forall (?o1 - object)
      (not (and (handempty) (holding ?o1)))))

@@

;;;
;;; Invariants with two quantified variable and size 2
;;;
(:derived (invariant-2-1)
  (forall (?o1 ?o2 - object)
      (not (and (on ?o1 ?o2) (holding ?o1)))))

@@

(:derived (invariant-2-5)
  (forall (?o1 ?o2 - object)
      (not (and (on ?o1 ?o2) (on ?o2 ?o1)))))
\end{lstlisting}
\end{subfigure}%

@@

\section{Learning \strips\ action models with planning}
Our approach for addressing the learning task $\Lambda$, is compiling it into a classical planning task with conditional effects. The intuition behind the compilation is that a solution to the resulting classical planning task is a sequence of actions that:
\begin{enumerate}
\item Programs the \strips\ action model $\Xi$. A solution plan has a {\em prefix} that, for each $\xi\in\Xi$, determines the fluents from $F_v$ that belong to its $pre(\xi)$, $del(\xi)$ and $add(\xi)$ sets.
\item Validates the programmed \strips\ action model $\Xi$ in the given input knowledge (the sequences of states $\Sigma$, and $\Phi$ if available). For every $\sigma_t\in \Sigma$, a solution plan has a postfix that produces a final state $s_{n}^t$ starting from the corresponding initial state $s_0^t$ using the programmed action model $\Xi$. We call this process the validation of the programmed \strips\ action model $\Xi$, at the learning example {\small $1\leq t\leq \tau$}. %If information about the corresponding plan $\pi_t\in \Pi$ is available, then it is also used in the validation.
\end{enumerate}

@@

Now we are ready to formalize the compilations. We start with $\Lambda$, because it requires less input knowledge. Given a learning task $\Lambda=\tup{\Psi,\Sigma}$ the compilation outputs a classical planning task $P_{\Lambda}=\tup{F_{\Lambda},A_{\Lambda},I_{\Lambda},G_{\Lambda}}$:
\begin{itemize}
\item $F_{\Lambda}$ extends $F$ with:
\begin{itemize}
\item Fluents representing the programmed action model $pre_f(\xi)$, $del_f(\xi)$ and $add_f(\xi)$, for every $f\in F_v$ and $\xi \in \Xi$. If a fluent $pre_f(\xi)/del_f(\xi)/add_f(\xi)$ holds, it means that $f$ is a precondition/negative effect/positive effect in the \strips\ operator schema $\xi\in \Xi$. For instance, the preconditions of the $stack$ schema (Figure~\ref{fig:stack}) are represented by fluents {\small\tt pre\_holding\_stack\_$v_1$} and {\small\tt pre\_clear\_stack\_$v_2$}.
\item A fluent $mode_{prog}$ indicating whether the operator schemes are being programmed or validated (already programmed) and fluents $\{test_t\}_{1\leq t\leq \tau}$, indicating the example where the action model is being validated.
\end{itemize}
\item $I_{\Lambda}$ contains the fluents from $F$ that encode $s_0^1$ (the initial state of the first label), every $pre_f(\xi)\in F_{\Lambda}$ and $mode_{prog}$ set to true. Our compilation assumes that initially any operator schema is programmed with every possible precondition, no negative effect and no positive effect.
\item $G_{\Lambda}=\bigcup_{1\leq t\leq \tau}\{test_t\}$, indicates that the programmed action model is validated in all the learning examples.
\item $A_{\Lambda}$ contains actions of three kinds:
\begin{enumerate}
\item Actions for {\em programming} an operator schema $\xi\in\Xi$:
\begin{itemize}
\item Actions for {\bf removing} a {\em precondition} $f\in F_v$ from the action schema $\xi\in\Xi$.

@@

\item Actions for {\em applying} an already programmed operator schema $\xi\in\Xi$ bound with the objects $\omega\subseteq\Omega^{ar(\xi)}$. We assume operators headers are known so the binding of the operator schema is done implicitly by order of appearance of the action parameters, i.e. variables $pars(\xi)$ are bound to the objects in $\omega$ appearing at the same position. 
\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{apply_{\xi,\omega}})=&\{pre_{f}(\xi)\implies p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
\cond(\mathsf{apply_{\xi,\omega}})=&\{del_{f}(\xi)\}\rhd\{\neg p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{add_{f}(\xi)\}\rhd\{p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{mode_{prog}\}\rhd\{\neg mode_{prog}\}.
\end{align*}
\end{small}

\item Actions for {\em validating} the learning example {\tt\small $1\leq t\leq \tau$}.
\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{validate_{t}})=&G_t\cup\{test_j\}_{j\in 1\leq j<t}\\
&\cup\{\neg test_j\}_{j\in t\leq j\leq \tau}\cup \{\neg mode_{prog}\},\\
\cond(\mathsf{validate_{t}})=&\{\emptyset\}\rhd\{test_t\}.
\end{align*}
\end{small}
\end{enumerate}
\end{itemize}

@@

\subsection{Plan constraints}
\subsubsection{Learning from labeled plans.}
Here we augment the input knowledge with the actions executed by the observed agent.

@@

We extend the compilation to consider labeled plans. Given a learning task $\Lambda'=\tup{\Psi,\Sigma,\Pi}$, the compilation outputs a classical planning task $P_{\Lambda'}=\tup{F_{\Lambda'},A_{\Lambda'},I_{\Lambda'},G_{\Lambda'}}$ that extends $P_{\Lambda}$ as follows:
\begin{itemize}
\item $F_{\Lambda'}$ extends $F_{\Lambda}$ with $F_{\Pi}=\{plan(name(\xi),\Omega^{ar(\xi)},j)\}$, the fluents to code the steps of the plans in $\Pi$, where $F_{\pi_t}\subseteq F_{\Pi}$ encodes $\pi_t\in \Pi$. Fluents $at_j$ and $next_{j,j_2}$, {\small $1\leq j<j2\leq n$}, are also added to represent the current plan step and to iterate through the steps of a plan.
\item $I_{\Lambda'}$ extends $I_{\Lambda}$ with fluents $F_{\pi_1}$ plus fluents $at_1$ and $\{next_{j,j_2}\}$, {\small $1\leq j<j2\leq n$}, for indicating the plan step where the action model is validated. Goals are $G_{\Lambda'}=G_{\Lambda}=\bigcup_{1\leq t\leq \tau}\{test_t\}$, as in the original compilation.
\item With respect to $A_{\Lambda'}$.
\begin{enumerate}
\item The actions for {\em programming} the preconditions/effects of a given operator schema $\xi\in\Xi$ are the same.
\item The actions for {\em applying} an already programmed operator have an extra precondition $f\in F_{\Pi}$, that encodes the current plan step, and extra conditional effects $\{at_{j}\}\rhd\{\neg at_{j},at_{j+1}\}_{\forall j\in [1,n]}$ for advancing to the next plan step. This mechanism forces that these actions are only applied as in the example plans.
\item The actions for {\em validating} the current learning example have an extra precondition, $at_{|\pi_t|}$, to indicate that the current plan $\pi_t$ was fully executed and extra conditional effects to unload plan $\pi_{t}$ and load the next plan $\pi_{t+1}$:
\begin{small}
\begin{align*}
&\{\emptyset\}\rhd\{\neg at_{|\pi_t|},at_1\}, \{f\}\rhd\{\neg f\}_{f\in F_{\pi_t}}, \{\emptyset\}\rhd\{f\}_{f\in F_{\pi_t+1}}.
\end{align*}
\end{small}
\end{enumerate}
\end{itemize}

@@

\section{Conclusions}

>>>>

\title{Learning \strips\ Action Models from State-Constraints}

@@

\begin{abstract}
This paper presents a classical planning compilation for learning \strips\ action models from observations of plan executions. Interestingly the compilation is fed with a set of {\em state-constraints}, that bounds the space of possible action models, and does not require the precise executed actions in the observations of the plan executions. The output is a possible action \strips\ action model, that satisfies the given state-constraints. Last but not least, the paper shows that this compilation is also flexible to include further information about the observed plan executions and increase the accuracy of the learned models.  
\end{abstract}

@@

An alternative approach to the hand-coding of action models is learning them from observations of plan executions. This is a well-studied problem with sophisticated algorithms, like {\sc ARMS}~\cite{yang2007learning}, {\sc SLAF}~\cite{amir:alearning:JAIR08} or {\sc LOCM}~\cite{cresswell2013acquiring}. Motivated by recent advances on the synthesis of different kinds of generative models with classical planning~\cite{bonet2009automatic,segovia2016hierarchical,segovia2017generating}, this paper introduces an innovative approach for learning \strips\ action models from observations of plan executions that:
\begin{enumerate}
\item Does not require information about the the precise actions applied in the observed plan executions.
\item Can be defined as a classical planning compilation which opens the door to the bootstrapping of planning action models.
\item Is extensible to further information about the observed plan executions to improve the learned models.
\end{enumerate}

@@

\subsection{State-constraints}
A {\em state invariant} is a formula $\phi$ that holds in the initial state of a given classical planning problem, formally $I\models \phi$, and at any state reachable from that state~\cite{rintanen:schematicInvariants:AAAI2017}, for all states $s$ reachable from $I$ $s\models \phi$. State invariants are traditionally useful for making satisfiability planning and backward search more efficient~\cite{rintanen2014madagascar,alcazar2015reminder}.

A {\em mutex} (meaning mutually exclusive) is a particular case of state invariant that take the form of a binary clause and that represents that a pair of different properties cannot be simultaneously true. For instance in a three-blocks blocksworld, $on(block1,block2)$ and $on(block1,block3)$ are mutex because $block1$ can only be on top of a single block.

A {\em lifted invariant} is a state invariant defined using a first order formula over the predicates of a given planning domain~\cite{rintanen:schematicInvariants:AAAI2017}. A {\em Domain invariant} is a state invariant that hold for any possible initial state~\cite{kautz:mutex:IJCAI1999}, they are instance-independent and often they are lifted invariants.  For instance in the blocksworld, $\forall x,y,z\ (on(x,y)\wedge on(x,z)) \implies y=z$, is a domain and lifted invariant because a block can only be on top of a single block no matter the initial state of the classical planning problem and no matter the particular identity of the blocks.

\section{Learning \strips\ action models}
Learning \strips\ action models from fully available input knowledge, i.e. from plans where every action in the plan is available as well as its corresponding {\em pre-} and {\em post-states}, is straightforward. In this case, \strips\ operator schemes are derived lifting the literals that change between the pre and post-state of the corresponding action executions. Preconditions are derived lifting the minimal set of literals that appears in all the pre-states of the corresponding actions.

Here we formalize a more challenging learning task, where less input knowledge is available. This learning task corresponds to observing an agent acting in the world but watching only the results of its plan executions. No information about the particular actions is given. This learning task is formalized as $\Lambda=\tup{\Psi,\Sigma,\Phi}$:
\begin{itemize}
\item $\Psi$ is the set of predicates that define the abstract state space of a given planning domain.
\item $\Sigma=\{\sigma_1,\ldots,\sigma_{\tau}\}$ is a set of state sequences $\sigma_t=(s_0^t,s_1^t,\ldots,s_{n}^t)$, {\tt\small $1\leq t\leq \tau$}, that comprises the states resulting from executing an unknown plan $\pi_t=\tup{a_1^t, \ldots, a_n^t}$ starting from the {\em initial} state $s_0^t$.
\item $\Phi$ is a set of {\em lifted domain mutex}.
\end{itemize}

A solution to $\Lambda$ is a set of operator schema $\Xi$ that is compliant with the predicates in $\Psi$, the given states sequences in $\Sigma$ and the set of state constraints $\Phi$. In this learning scenario, a solution must not only determine a possible \strips\ action model but also the content of the plans $\pi_t$, {\tt\small $1\leq t\leq \tau$} that explain $\Sigma$ and $\Phi$ with the learned \strips\ model.

@@

\begin{footnotesize}
\begin{subfigure}{.6\textwidth}
{\tt ;;; Lifted domain mutexes in $\Phi$}
\begin{verbatim}
(:derived (invariant-1-1)
  (forall (?o1 - object)
      (not (and (handempty) (holding ?o1)))))

@@

(:derived (invariant-2-1)
  (forall (?o1 ?o2 - object)
      (not (and (on ?o1 ?o2) (holding ?o1)))))

@@

(:derived (invariant-2-5)
  (forall (?o1 ?o2 - object)
      (not (and (on ?o1 ?o2) (on ?o2 ?o1)))))
\end{verbatim}
\end{subfigure}%
\end{footnotesize}

@@

\section{Learning \strips\ action models with planning}
Our approach for addressing the learning task $\Lambda$, is compiling it into a classical planning task with conditional effects. The intuition behind the compilation is that a solution to the resulting classical planning task is a sequence of actions that:
\begin{enumerate}
\item Programs the \strips\ action model $\Xi$. A solution plan has a {\em prefix} that, for each $\xi\in\Xi$, determines the fluents from $F_v$ that belong to its $pre(\xi)$, $del(\xi)$ and $add(\xi)$ sets.
\item Validates the programmed \strips\ action model $\Xi$ in the given input knowledge (the sequences of states $\Sigma$ and $\Phi$ formulae). For every $\sigma_t\in \Sigma$, a solution plan has a postfix that produces a final state $s_{n}^t$ starting from the corresponding initial state $s_0^t$ using the programmed action model $\Xi$. We call this process the validation of the programmed \strips\ action model $\Xi$, at the learning example {\small $1\leq t\leq \tau$}. %If information about the corresponding plan $\pi_t\in \Pi$ is available, then it is also used in the validation.
\end{enumerate}

@@

Now we are ready to formalize the compilation. Given a learning task $\Lambda=\tup{\Psi,\Sigma}$ the compilation outputs a classical planning task $P_{\Lambda}=\tup{F_{\Lambda},A_{\Lambda},I_{\Lambda},G_{\Lambda}}$:
\begin{itemize}
\item $F_{\Lambda}$ extends $F$ with:
\begin{itemize}
\item Fluents representing the programmed action model $pre_f(\xi)$, $del_f(\xi)$ and $add_f(\xi)$, for every $f\in F_v$ and $\xi \in \Xi$. If a fluent $pre_f(\xi)/del_f(\xi)/add_f(\xi)$ holds, it means that $f$ is a precondition/negative effect/positive effect in the \strips\ operator schema $\xi\in \Xi$. For instance, the preconditions of the $stack$ schema (Figure~\ref{fig:stack}) are represented by fluents {\small\tt pre\_holding\_stack\_$v_1$} and {\small\tt pre\_clear\_stack\_$v_2$}.
\item A fluent $mode_{prog}$ indicating whether the operator schemes are being programmed or validated (already programmed) and fluents $\{test_t\}_{1\leq t\leq \tau}$, indicating the example where the action model is being validated.
\item Fluents, $at_j$ and $next_{j,j_2}$, {\small $1\leq j<j2\leq n$}, to code the obsevation steps and iterate through them.
\end{itemize}
\item $I_{\Lambda}$ contains the fluents from $F$ that encode $s_0^1$ (the initial state of the first label), fluents $at_1$ and and $\{next_{j,j_2}\}$, {\small $1\leq j<j2\leq n$}, for indicating the step where the action model is validated and every $pre_f(\xi)\in F_{\Lambda}$ and $mode_{prog}$ set to true. Our compilation assumes that initially any operator schema is programmed with every possible precondition, no negative effect and no positive effect.
\item $G_{\Lambda}=\bigcup_{1\leq t\leq \tau}\{test_t\}$, indicates that the programmed action model is validated in all the learning examples.
\item $A_{\Lambda}$ contains actions of three kinds:
\begin{enumerate}
\item Actions for {\em programming} an operator schema $\xi\in\Xi$:
\begin{itemize}
\item Actions for {\bf removing} a {\em precondition} $f\in F_v$ from the action schema $\xi\in\Xi$.

@@

\item Actions for {\em applying} an already programmed operator schema $\xi\in\Xi$ bound with the objects $\omega\subseteq\Omega^{ar(\xi)}$. We assume operators headers are known so the binding of the operator schema is done implicitly by order of appearance of the action parameters, i.e. variables $pars(\xi)$ are bound to the objects in $\omega$ appearing at the same position. 
\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{apply_{\xi,\omega}})=&\{pre_{f}(\xi)\implies p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
\cond(\mathsf{apply_{\xi,\omega}})=&\{del_{f}(\xi)\}\rhd\{\neg p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{add_{f}(\xi)\}\rhd\{p(\omega)\}_{\forall p\in\Psi,f=p(pars(\xi))},\\
&\{at_{j}\}\rhd\{\neg at_{j},at_{j+1}\}_{\forall j\in [1,n]},\\
&\{mode_{prog}\}\rhd\{\neg mode_{prog}\}.
\end{align*}
\end{small}

\item Actions for {\em validating} the learning example {\tt\small $1\leq t\leq \tau$}. 
\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{validate_{t}})=&G_t\cup\{test_j\}_{j\in 1\leq j<t}\\
&\cup\{\neg test_j\}_{j\in t\leq j\leq \tau}\cup \{\neg mode_{prog}\},\\
\cond(\mathsf{validate_{t}})=&\{\emptyset\}\rhd\{test_t\},\\
&\{\emptyset\}\rhd\{\neg at_{|\pi_t|},at_1\}.
\end{align*}
\end{small}
\end{enumerate}
\end{itemize}

@@

\subsection{Plan constraints}

Here we augment the input knowledge with the actions executed by the observed agent, when available.

@@

We extend the compilation to consider the actions in the executed plans. Given a learning task $\Lambda'=\tup{\Psi,\Sigma,\Phi,\Pi}$, the compilation outputs a classical planning task $P_{\Lambda'}=\tup{F_{\Lambda'},A_{\Lambda'},I_{\Lambda'},G_{\Lambda'}}$ that extends $P_{\Lambda}$ as follows:
\begin{itemize}
\item $F_{\Lambda'}$ extends $F_{\Lambda}$ with $F_{\Pi}=\{plan(name(\xi),\Omega^{ar(\xi)},j)\}$, the fluents to code the steps of the plans in $\Pi$, where $F_{\pi_t}\subseteq F_{\Pi}$ encodes $\pi_t\in \Pi$. 
\item $I_{\Lambda'}$ extends $I_{\Lambda}$ with fluents $F_{\pi_1}$. Goals are $G_{\Lambda'}=G_{\Lambda}=\bigcup_{1\leq t\leq \tau}\{test_t\}$, as in the original compilation.
\item With respect to $A_{\Lambda'}$.
\begin{enumerate}
\item The actions for {\em programming} the preconditions/effects of a given operator schema $\xi\in\Xi$ are the same.
\item The actions for {\em applying} an already programmed operator have an extra precondition $f\in F_{\Pi}$, that encodes the current plan step. This mechanism forces that these actions are only applied as in the example plans.
\item The actions for {\em validating} the current learning example have an extra conditional effects to unload plan $\pi_{t}$ and load the next plan $\pi_{t+1}$:
\begin{small}
\begin{align*}
&\{f\}\rhd\{\neg f\}_{f\in F_{\pi_t}}, \{\emptyset\}\rhd\{f\}_{f\in F_{\pi_t+1}}.
\end{align*}
\end{small}
\end{enumerate}
\end{itemize}

@@

\subsection{Learning with state-constraints}
For each domain we provide a set of {\em lifted domain mutex},  lifted domain invariants that takes the form of a binary clauses. For instance, in the blocksworld $\forall x,y$ then $clear(x)$ and $on(x,y)$ is a {\em lifted domain mutex}.

\subsection{Learning with plans}

\section{Conclusions}
{\em Linear Temporal Logic} (LTL) also includes model operator that also allows to represent state constraints~\cite{haslum:LTL:ecai10}. For instance the {\em always} operator, denoted by $\square$, defines constraints that, like {\em lifted domain invariants}, must be true at any reachable state.
